---
title: "Jonis R Notebook"
output: html_document
---

The [R plugin](https://www.jetbrains.com/help/pycharm/r-plugin-support.html) for IntelliJ-based IDEs provides
handy capabilities to work with the [R Markdown](https://www.jetbrains.com/help/pycharm/r-markdown.html) files.
To [add](https://www.jetbrains.com/help/pycharm/r-markdown.html#add-code-chunk) a new R chunk,

```{r}
pacman::p_load(tidyverse, readxl, lubridate, RColorBrewer, ggthemes, unikn)
# data <- read_csv("data.txt")
# runner <- read_csv("../workout.csv")
library(readr)
#data <- read_csv("../data.csv")
data <- read_csv("../dataLong.csv")
View(dataLong)

```

```{r}
# Transform the values in the date-column into a date format
#data$date <- as.Date( data$date, format = "%d.%m.%Y")

library(lubridate)
data$date <- parse_date_time(data$date, c("dmy"))
data$month <- parse_date_time(data$month, c("my"))
#data$time <- parse_date_time(data$time, c("HMS"))

# Using functions provided by the `lubridate` -package, we transform the values in the month-columns into a date format:

data$weekday <- weekdays(data$date)

data$amount <- 1

#Using the `weekdays` -function we can add a column "weekday" that contains the day of the week corresponding to the date:
```



```{r}
# Convert the date column to a proper date format
#data$date <- as.Date(data$date)

# Create a sequence of dates for the last 12 months
last_12_months <- seq(Sys.Date(), by = "-1 month", length.out = 12)

# Create a data frame with a column for each month and initialize to zero
months <- data.frame(matrix(0, nrow = 1, ncol = length(last_12_months)))
colnames(months) <- format(last_12_months, "%b %Y")

# Loop over the rows in data and update the corresponding month in months
for (i in 1:nrow(data)) {
  month_name <- format(data$date[i], "%b %Y")
  if (month_name %in% colnames(months)) {
    months[1, month_name] <- months[1, month_name] + 1
  }
}


```

```{r}
library(ggplot2)

# Convert the months data frame to long format
months_long <- tidyr::gather(months, month, days, factor_key = TRUE)

# Create a bar chart
ggplot(months_long, aes(x = month, y = days, fill = month)) +
  geom_bar(stat = "identity") +
  scale_fill_discrete(name = "Month", labels = format(last_12_months, "%b %Y")) +
  xlab("Month") +
  ylab("Number of days")
```



```{r}
data %>%
  ggplot(mapping = aes(x = month,
                       y = amount,
                        fill = weekday)) +
  labs(x = "month", y = "total amount") +
  geom_col() +
  theme_classic()
```


```{r}
#plot the amount of events per moth:
ggplot(data, aes(x=month, y=amount,fill=weekday)) +
  geom_bar(stat='identity') +
  xlab('Month') +
  ylab('Number of Events') +
  ggtitle('Number of Events Per Month')
```
(Language R)
given the following data frame called "data":
each line represents an amount.
The Column "date" contains the date of the month in a date format.
The Column "month" contains the month if the event in a date format.
The Column "weekday" contains the weekday of the event as a String.
weekday = {"Montag", "Dienstag", "Mittwoch", "Donnerstag", "Freitag", "Samstag","Sonntag"}

plot the amount of events per weekday, fill = month. make sure that the x-achis is sorted.
add the median value of the amount to the plot. increase the text size on the x and y axis:

```{r}
data %>%
  ggplot(mapping = aes(x = weekday,
                       y = amount,
                       fill = month)) +
  labs(x = "weekady", y = "total amount") +
  geom_col() +
  theme_classic()


library(ggplot2)

ggplot(data, aes(x = weekday, y = amount, fill = month)) +
  geom_bar(stat = "identity") +
    theme(axis.text.x = element_text(size = 8),
          axis.text.y = element_text(size = 8))  +
  scale_x_discrete(limits = c("Montag", "Dienstag", "Mittwoch", "Donnerstag", "Freitag", "Samstag", "Sonntag")) +
  geom_hline(aes(yintercept = median(amount)), color = "red")


# library(ggplot2)
#
# ggplot(data, aes(x=weekday, y=amount, fill=month)) +
#   geom_boxplot() +
#  # geom_text(aes(label = round(median(amount),2)), hjust = 0.5, vjust = -0.5, size = 8) +
#   scale_x_discrete(limits = c("Montag", "Dienstag", "Mittwoch", "Donnerstag", "Freitag", "Samstag", "Sonntag")) +
#   theme(axis.text.x = element_text(size = 8),
#         axis.text.y = element_text(size = 8))
```



```{r}
# Libraries
library(ggplot2)
library(dplyr)
library(hrbrthemes)

# Dummy data
# data <- data.frame(
#   day = as.Date("2017-06-14") - 0:364,
#   value = runif(365) - seq(-140, 224)^2 / 10000
# )

# Most basic bubble plot
p <- ggplot(months_long, aes(x=month, y=days)) +
  geom_line( color="#69b3a2") +
  xlab("") +
  theme_ipsum() +
  theme(axis.text.x=element_text(angle=60, hjust=1))

p
```



```{r}
# Libraries
library(ggplot2)
library(dplyr)
library(hrbrthemes)

# Dummy data
dataa <- data.frame(
  day = as.Date("2017-06-14") - 0:364,
  value = runif(365) + seq(-140, 224)^2 / 10000
)

# Most basic bubble plot
#p <- ggplot(dataa, aes(x = day, y = value)) +
p <- ggplot(months_long, aes(x = months, y = days)) +
  geom_line( color="blue") +
  geom_point() +
  xlab("") +
  theme_ipsum() +
  theme(axis.text.x=element_text(angle=60, hjust=1)) +
  #scale_x_date(limit=c(as.Date("2022-04-01"),as.Date("2023-03-01"))) +
  ylim(0,1.5)

p
```

```{r}
# Create a bubble plot
ggplot(months_long, aes(x = month, y = 1, size = days, fill = month)) +
  geom_point(shape = 21) +
  scale_size(range = c(5, 15)) +
  scale_fill_discrete(name = "Month", labels = format(last_12_months, "%b %Y")) +
  xlab("Month") +
  ylab("") +
  guides(size = FALSE)
```



```{r}
run <- read_csv("runner.txt")
```

read distance 2
```{r}
# dwr <- read_csv(sep = ";", header = TRUE,"DistanceWalkingRunning2")
dwr <- read.csv("../workout.csv", sep=";")
distanceWalkingRunning4 <- read.csv("../dwr.csv", sep=";")
library(lubridate)

dwr$start <- as.Date(dwr$start, format="%Y-%m-%d %H:%M:%S %z")
distanceWalkingRunning4$startDate <- as.Date(distanceWalkingRunning4$startDate, format="%Y-%m-%d %H:%M:%S %z")
```

```{r}
dwr %>%
ggplot(mapping = aes(x = start,
                     y = value,
                     fill = unit)) +
  labs(x = "day", y = "distance") +
  geom_col() +
  theme_classic() +
  facet_wrap(~type,
             scale = "free")

dwr %>%
  ggplot(mapping = aes(x = start,
                       y = value,
                       fill = type)) +
  labs(x = "day", y = "distance") +
  geom_col() +
  theme_classic() +
  facet_wrap(~unit,
             scale = "free")
```


```{r}
distanceWalkingRunning4 %>%
  ggplot(mapping = aes(x = startDate,
                       y = sum,
                       fill = unit)) +
  labs(x = "day", y = "distance") +
  geom_col() +
  theme_classic() +
  facet_wrap(~type,
             scale = "free")

distanceWalkingRunning4 %>%
  ggplot(mapping = aes(x = startDate,
                       y = sum,
                       fill = type)) +
  labs(x = "day", y = "distance") +
  geom_col() +
  theme_classic() +
  facet_wrap(~unit,
             scale = "free")
```



```{r}
run %>%
  ggplot(mapping = aes(x = "athlete's nationality",
                       y = time)) +
  geom_col() +
  theme_minimal()
```
```{r}
df <- swiss[c("Examination", "Education", "Infant.Mortality")]
#create a new dataframe. First column is "Examination", second "Education", last "Infant.Mortality".
df <- df[c(1, 2, 3, 10, 11, 12, 13),]
#create a new dataframe with the rows 1, 2, 3, 10, 11, 12, 13
```
```{r}
# Bar plot
df %>%
  ggplot(mapping = aes(y = "Infant.Mortality")) +
  geom_col() +
  theme_minimal()

```
position the caret at any line or the code chunk, then click "+".

The code chunk appears:
```{r}
```

Type any R code in the chunk, for example:
```{r}
mycars <- within(mtcars, { cyl <- ordered(cyl) })
mycars
```

Now, click the **Run** button on the chunk toolbar to [execute](https://www.jetbrains.com/help/pycharm/r-markdown.html#run-r-code) the chunk code. The result should be placed under the chunk.
Click the **Knit and Open Document** to build and preview an output.