---
title: "Jonis R Notebook"
output: html_document
---

The [R plugin](https://www.jetbrains.com/help/pycharm/r-plugin-support.html) for IntelliJ-based IDEs provides
handy capabilities to work with the [R Markdown](https://www.jetbrains.com/help/pycharm/r-markdown.html) files.
To [add](https://www.jetbrains.com/help/pycharm/r-markdown.html#add-code-chunk) a new R chunk,
```{r}
run <- read_csv("runner.txt")


```


```{r}
run %>%
  ggplot(mapping = aes(x = "athlete's nationality",
                       y = time)) +
  geom_col() +
  theme_minimal()
```
```{r}
df <- swiss[c("Examination", "Education", "Infant.Mortality")]
#create a new dataframe. First column is "Examination", second "Education", last "Infant.Mortality".
df <- df[c(1, 2, 3, 10, 11, 12, 13),]
#create a new dataframe with the rows 1, 2, 3, 10, 11, 12, 13
```
```{r}
# Bar plot
df %>%
  ggplot(mapping = aes(y = "Infant.Mortality")) +
  geom_col() +
  theme_minimal()

```
position the caret at any line or the code chunk, then click "+".

The code chunk appears:
```{r}
```

Type any R code in the chunk, for example:
```{r}
mycars <- within(mtcars, { cyl <- ordered(cyl) })
mycars
```

Now, click the **Run** button on the chunk toolbar to [execute](https://www.jetbrains.com/help/pycharm/r-markdown.html#run-r-code) the chunk code. The result should be placed under the chunk.
Click the **Knit and Open Document** to build and preview an output.